Empirical Evaluation of eval in R

### 2020-08-27 inst/analysis/analysis_stable.Rmd
Fixes

@@

eval_calls <- bind_rows(eval_calls_packages, eval_call_core)

# A flexible way to document the dataset: it is quick and easy to document a new column
c_names <- names(eval_calls)
column_names <- setNames(data.frame(matrix(ncol = length(c_names), nrow = 0)), c_names)

@@

```{r}
ast_sizes <- eval_calls %>% slice_sample(n=10000) %>% mutate(expr_resolved_ast_size = map_int(expr_resolved, expr_size_str))
```

```{r}
# ast_sizes %>% ggplot(aes(x = expr_resolved_ast_size, weight = nb_ev_calls, group = dataset)) +
#   geom_histogram(aes(y = stat(width*density)), na.rm = TRUE, binwidth = 0.1) +
#   scale_x_log10() +  scale_y_sqrt(labels=scales::percent) +
#   labs(x = "AST size", y = "relative frequencies")

# ast_sizes %>% 
#   ggplot(aes(x = dataset, y = expr_resolved_ast_size, fill = dataset, weight = nb_ev_calls)) +
#   geom_flat_violin(trim=FALSE, width=.5) +
#   geom_dotplot(
#     binaxis="y", 
#     dotsize=0.01, 
#     stackdir="down", 
#     binwidth=0.01, 
#     position=position_nudge(-0.025)) +
#   scale_y_log10(labels = scales::comma) +
#   labs(y="AST size (log)") +
#   theme(
#     legend.box="horizontal",
#     axis.title.x=element_blank()
#   )

ast_sizes %>%
  ggplot(aes(x = dataset, y = expr_resolved_ast_size, fill = dataset, weight = nb_ev_calls)) +
  geom_violin(trim = FALSE, width=.5)+
  geom_boxplot(width=.05) +
  scale_y_log10(labels = scales::comma) +
  labs(y="AST size (log)") +
  theme(
    legend.box="horizontal",
    axis.title.x=element_blank()
  )

ggsave(path(PLOT_DIR, "ast_sizes.pdf"))
```

@@

>>>>

now <- Sys.time()

@@

eval_calls_raw <- bind_rows(eval_calls_packages, eval_call_core)
```

We remove a few columns we do not need here and deduplicate.
```{r deduplicate}
eval_calls <- eval_calls_raw %>% count(across(-c(builtin:indirect_allocation)), name = "nb_ev_calls2") %>%
    mutate(nb_ev_calls = nb_ev_calls * nb_ev_calls2) %>% 
    select(-nb_ev_calls2)
```

```{r document}
# A flexible way to document the dataset: it is quick and easy to document a new column
c_names <- names(eval_calls)
column_names <- setNames(data.frame(matrix(ncol = length(c_names), nrow = 0)), c_names)

@@

```{r}
ast_sizes <- eval_calls %>% slice_sample(n=10000) %>% mutate(expr_resolved_nodes = map_int(expr_resolved, expr_size_str))
# Now precomputed during the tracing
#ast_sizes <- eval_calls
```

```{r}
# ast_sizes %>% ggplot(aes(x = expr_resolved_nodes, weight = nb_ev_calls, group = dataset)) +
#   geom_histogram(aes(y = stat(width*density)), na.rm = TRUE, binwidth = 0.1) +
#   scale_x_log10() +  scale_y_sqrt(labels=scales::percent) +
#   labs(x = "AST size", y = "relative frequencies")

# ast_sizes %>% 
#   ggplot(aes(x = dataset, y = expr_resolved_nodes, fill = dataset, weight = nb_ev_calls)) +
#   geom_flat_violin(trim=FALSE, width=.5) +
#   geom_dotplot(
#     binaxis="y", 
#     dotsize=0.01, 
#     stackdir="down", 
#     binwidth=0.01, 
#     position=position_nudge(-0.025)) +
#   scale_y_log10(labels = scales::comma) +
#   labs(y="AST size (log)") +
#   theme(
#     legend.box="horizontal",
#     axis.title.x=element_blank()
#   )

ast_sizes %>%
  ggplot(aes(x = dataset, y = expr_resolved_nodes, fill = dataset, weight = nb_ev_calls)) +
  geom_violin(trim = FALSE, width=.5)+
  geom_boxplot(width=.05) +
  scale_y_log10(labels = scales::comma) +
  labs(y="AST size (log)") +
  theme(
    legend.box="horizontal",
    axis.title.x=element_blank()
  )

ggsave(path(PLOT_DIR, "ast_sizes.pdf"))

ast_sizes_prop <- ast_sizes %>% count(expr_resolved_nodes, wt = nb_ev_calls) %>%
                      mutate(proportion = n / sum(n)) %>% 
                      arrange(expr_resolved_nodes) %>% 
                      mutate(cumulative = cumsum(proportion))

ast_size_one <- ast_sizes %>% filter(expr_resolved_nodes == 1) 
nb_ast_size_one <- count(ast_size_one, wt = nb_ev_calls)$n
nb_ast_size_one_call_sites <- nb_eval_call_sites(ast_size_one)
r("nb ast one percent", ratio(nb_ast_size_one, sum(ast_sizes_prop$n)))
r("nb ast one call site percent", ratio(nb_ast_size_one_call_sites, nb_eval_call_sites(ast_sizes)))

nb_nodes_many <- ast_sizes_prop %>% filter(cumulative >= 0.95) %>% .[1,]

r("ast size nine five", nb_nodes_many$expr_resolved_nodes)
r("ast size nine five exact percent", percent(nb_nodes_many$cumulative))

@@

```{r}
duration <- difftime(Sys.time(), now)
```

Notebook execution was `r duration` `r units(duration)`.
